---
title: 'R Course: Lesson 1 - R Basics'
author: "Page Piccinini"
date: "February 11, 2016"
output: pdf_document
---
```{r}
load("rcourse_lesson1_environment.RData")
```

# Data

Here is a look at our two data frames. First is the one we read in, the second is our subset of just the bilinguals' data.

```{r}
head(data)
head(data_bl)
```

# Figures

Here's a figure of the bilinguals compared to the monolinguals.

```{r, fig.align='center'}
data.plot
```

Here's a figure of the bilinguals separted by L2 proficiency.

```{r, fig.align='center'}
data_bl.plot
```

# Descriptive Statistics

When looking at the summary statistics by group, bilinguals have much more variance than monolinguals.

```{r}
data_sum
```

However, when summarising within type of bilingual (level of L2 proficiency) we see where the variance comes from.

```{r}
data_bl_sum
```

To show how all three groups compare we can make a final figure with the bilinguals separated out by L2 profiency and still include the monolinguals.

```{r, fig.align='center'}
data_blwml.plot
```